### 2009-04-07 talk/icooolps2009-dotnet/clibackend.tex
fix two XXXs

\subsubsection{Implementation of flexswitches}
Finally, we can have a look at the implementation of flexswitches.
The following snippet shows the special case of integer flexswitches.
\begin{lstlisting}[language={[Sharp]C}] 
public class IntLowLevelFlexSwitch: 
                        BaseLowLevelFlexSwitch {
  public uint default_blockid = 0xFFFFFFFF;
  public int numcases = 0;
  public int[] values = new int[4];
  public FlexSwitchCase[] cases = 
                          new FlexSwitchCase[4];

@@

XXX: add note to explain why we use a for loop instead of an hashtable

XXX: add note to explain who calls execute()

@@

The most interesting part is the body of method \lstinline{execute},
which takes a value and a set of input arguments to be passed across
the link and jumps to the right block by performing a linear search in
array \lstinline{values}.

>>>>

\subsubsection{Implementation of flexswitches}

To implement each flexswitch, the CLI backend creates an instace of a subclass
of \lstinline{BaseLowLevelFlexSwitch}: such an instance stores the mapping
between each value and the corresponding method we want to invoke.  Then, the
generated code contains a call to the method \lstinline{execute}, which
selects and invoke the right method depending on the actual value we are
switching on.

The following snippet shows the special case of integer flexswitches.
\begin{lstlisting}[language={[Sharp]C}] 
public class IntLowLevelFlexSwitch: 
                        BaseLowLevelFlexSwitch {
  public uint default_blockid = 0xFFFFFFFF;
  public int numcases = 0;
  public int[] values = new int[4];
  public FlexSwitchCase[] cases = 
                          new FlexSwitchCase[4];

@@

@@

The most interesting part is the body of method \lstinline{execute},
which takes a value and a set of input arguments to be passed across
the link and jumps to the right block by performing a linear search in
array \lstinline{values}\footnote{Our microbenchmarks indicate that a linear
search is the fastest way to find the right method to call, since typically
each flexswitch contains only a very small number of cases.}.
